---
title: "Conceptual Questions"
format: html
toc: TRUE
editor_options: 
  chunk_output_type: inline
---

## Task 1: Answer questions

#### 1. If your working directory is myfolder/homework/, what relative path would you specify to get the file located at myfolder/MyData.csv?

read.csv("MyData.csv")

#### 2. What are the major benefits of using R projects?

R Projects are easy to create and provide a straightforward way to divide work into multiple contexts, including a working directory, work space, history, and folder structure and source documents. As long as we've used relative paths in our R Project, we can also share the Project with other users, who will easily be able to work seamlessly on the project. Other users will have to download and install any version of R packages, as packages are specific to a computer and not automatically transferred along with a project.

#### 3. What is git and what is github?

Git is version control software. GitHub is a web interface that makes it easy to use Git for version control and to collaborate with other people by sharing code and more.

#### 4. What are the two main differences between a tibble and a data.frame?

data.frame is a function in R to create a data frame. A tibble is used in tidyverse. A tibble is a more modern version of a data frame. Data frame prints all the columns and can print a very large output if the dataset is big. A tibble prints only the first 10 rows and fits the output to your screen width. This makes it much more user-friendly for large datasets. The most important difference between tibbles and data frames is the way tibbles print; they are designed for large datasets, so they only show the first few rows and only the columns that fit on one screen.

#### 5. Rewrite the following nested function call using BaseR’s chaining operator:

-   arrange(filter(select(as_tibble(iris), starts_with("Petal"), Species), Petal.Length \< 1.55), Species)

```{r}
  as_tibble(iris) |>
    select(starts_with("Petal"), Species) |>
    filter(Petal.Length < 1.55) |>
    arrange(Species)

```

## Task 2: Tidyverse

```{r}

library(tidyverse)
```

download data from URL and save

```{r}
# read in data from URL and specify col names
glass_data <- read_csv("https://www4.stat.ncsu.edu/~online/datasets/glass.data", col_names = c("ID","RI","Na","Mg","Al","Si","K","Ca","Ba","Fe","TypeOfGlass"))
glass_data


```

mutate

```{r}

library(dplyr)

glass_data2 <- glass_data |>
  mutate(
    TypeOfGlass = case_when(
      TypeOfGlass == 1 ~ "building_windows_float_processed",
      TypeOfGlass == 2 ~ "building_windows_non_float_processed",
      TypeOfGlass == 3 ~ "vehicle_windows_float_processed",
      TypeOfGlass == 4 ~ "vehicle_windows_non_float_processed",
      TypeOfGlass == 5 ~ "containers",
      TypeOfGlass == 6 ~ "tablewares",
      TypeOfGlass == 7 ~ "headlamps",
      TRUE             ~ "other"
    )
  ) |>
 filter(Fe < 0.2) |>
  filter(TypeOfGlass == "tablewares" | TypeOfGlass == "headlamps")
   
glass_data2
```

Yeast

